Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-07-14 main.tex
abstract suggestion
add citation
Add reference for noisy and probabilistic ending.

\begin{abstract}
    We present tournament results and several powerful strategies for the Iterated
    Prisoner's Dilemma created using reinforcement learning techniques
    (evolutionary and particle swarm algorithms). These strategies are
    trained to perform well against a corpus of over 170 distinct
    opponents, including many well-known and classic strategies. All
    the trained strategies win standard tournaments against the total collection
    of other opponents. The trained strategies and one particular human made
    designed strategy are the top performers in noisy tournaments also.
\end{abstract}

@@

Since Robert Axelrod's seminal tournament \cite{Axelrod1980a}, a number of
IPD\@ tournaments have been undertaken and are summarised in
Table~\ref{tbl:tournaments}. Further to the work described in
\cite{knight2016open} a regular set of standard, noisy and probabilistic ending
tournaments are carried out as more strategies are added to the Axelrod library.
Details and results are available here:
\url{http://axelrod-tournament.readthedocs.io}. This work presents a detailed
analysis of a tournament with 176 strategies (details given
in Section~\ref{sec:results}).

>>>>

\begin{abstract}
    We present tournament results and several powerful strategies for the Iterated
    Prisoner's Dilemma created using reinforcement learning techniques
    (evolutionary and particle swarm algorithms). These strategies are
    trained to perform well against a corpus of over 170 distinct
    opponents, including many well-known and classic strategies. All
    the trained strategies win standard tournaments against the total collection
    of other opponents. The trained strategies and one particular human made
    designed strategy are the top performers in tournaments where also noise is introduced.
\end{abstract}

@@

Since Robert Axelrod's seminal tournament \cite{Axelrod1980a}, a number of
IPD\@ tournaments have been undertaken and are summarised in
Table~\ref{tbl:tournaments}. Further to the work described in
\cite{knight2016open} a regular set of standard, noisy~\cite{Bendor1991} and 
probabilistic ending~\cite{Axelrod1980b} tournaments are carried out as more 
strategies are added to the Axelrod library.
Details and results are available here:
\url{http://axelrod-tournament.readthedocs.io}. This work presents a detailed
analysis of a tournament with 176 strategies (details given
in Section~\ref{sec:results}).
